Covariant Phase Space via MultiSymplectic Geometry

### 2017-05-26 cpsviams.tex
Updating illustrations

\usepackage{graphicx}
\usepackage{wrapfig}

@@

\begin{abstract}
In questo talk viene dettagliata la costruzione del covariant phase space partendo dal formalismo multisimplettico come descritto nell'artticolo di forger romero.

La costruzione del covariant phase space con la cognizione del formalismo simplettico come descritta nell'articolo di forger romero.

Piccola rivisisazione sulla dimostrazione della corrente simplettica (indipendentemente dal formalismo adottato)

Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.

@@

Again, we would like to employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
\begin{notation}
	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on different order jet bundle over $F$, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
\begin{displaymath}
	D[\; ] = \; \Gamma^\infty(F) \ni \phi \quad \mapsto \quad D[ \phi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear F \right)\right)
\end{displaymath}	
in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
//
	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
	\begin{displaymath}
		\left\langle D[\phi] \right\vert \left. V \right\rangle =
		\phi^\ast \left( i_V \omega \right) 
		\begin{cases}
			(j^1 \varphi)^\ast \left( i_{j^1V} \: \omega_\Lagrangian \right) \\
			(\varphi, \pi)^\ast \left( i_V \: \omega_\Hamiltonian \right)
		\end{cases}              
        \in \Omega^m(M)
	\end{displaymath}

@@

\begin{figure}
\centering
\includegraphics[width=0.40\textwidth]{Pictures/sigma.png}
  %\caption{.}
\end{figure}
Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$

\begin{figure}
  \centering
  \includegraphics[width=0.41\textwidth]{Pictures/fieldJacobi.png}
  \caption{.}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{hyperref}

@@

\begin{abstract}
In this talk we detail the construction of the covariant phase space starting from multisymplectic framework of geometric classic field theories following essentially the paper written by forger romero. 
%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.

@@

Again, we would like to employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
\begin{notation}
	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on different order jet bundle over $F$, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
\begin{displaymath}
	D[\; ] = \; \Gamma^\infty(F) \ni \phi \quad \mapsto \quad D[ \phi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear F \right)\right)
\end{displaymath}	
in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
\\
	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
	\begin{displaymath}
		\left\langle D[\phi] \right\vert \left. V \right\rangle =
		\phi^\ast \left( i_V \omega \right) 
		\begin{cases}
			(j^1 \varphi)^\ast \left( i_{j^1V} \: \omega_\Lagrangian \right) \\
			(\varphi, \pi)^\ast \left( i_V \: \omega_\Hamiltonian \right)
		\end{cases}              
        \in \Omega^m(M)
	\end{displaymath}

@@

\begin{figure}
\centering
  \includestandalone[mode=buildnew]{sigma}
  %\caption{.}
\end{figure}
Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$

\begin{figure}
  \centering
    \includestandalone[mode=buildnew]{fieldJacobi}
  %\caption{.}
\end{figure}

### 2017-05-26 sigma.tex
Updating illustrations

\documentclass[border=10pt, tikz]{standalone}
\usepackage{tikz}
\usepackage{tikz-3dplot}
        \usetikzlibrary{patterns,hobby}

@@

\draw[W] (O2.center) -- node [below] {} (A2.center); 
\draw[W] (A2.center) --  node [right] {} (B2.center);
\draw[W] (B2.center) --  node [right] {} (C2.center); 
\draw[W] (C2.center) --  node [above] {$W$} (O2.center);

\draw[W] (O.center) -- node [below] {} (O2.center); 
\draw[W] (A.center) -- node [below] {} (A2.center); 
\draw[W] (B.center) -- node [below] {} (B2.center); 
\draw[W,hidden] (C.center) -- node [below] {} (C2.center);

@@

\node (P1) at (1.5,3,\zlevel) {};
\node (P2) at (2.5,3,2.75)  {};
\node (P3) at (1.5,3,2.75)  {};
\draw[-latex,orange] (P1.center) -- node [right] {$V$}	 (P2.center);
\draw[-latex,orange!85] (P1.center) -- node [left] {$\sigma(V)$} (P3.center);
\draw[-latex,dashed,line width=0.5pt,dashed] (P2.center) -- node [above] {$\sigma$} (P3.center);

\node[label={270:{$0(e)$}},circle,fill,inner sep=1pt] (0e) at (1.5,3,\zlevel) {};
\node[label={270:{$e$}},circle,fill,inner sep=1pt] (e) at (1.5,3,0)  {};
\node[label={270:{$x$}},circle,fill,inner sep=1pt] (x) at (0,3,0)  {};

\path[fill=green!5,opacity=.25] (B.center) to (A.center) to (A2.center) to (A2.center) to (B.center);
\path[fill=green!5,opacity=.25] (A.center) to (O.center) to (O2.center) to (O2.center) to (A.center);

@@

    	%Curva di Partenza
    \draw[red,line width=1pt] (1 ,0,\zlevel)
    .. controls (1.5,0.75,\zlevel)  and (2.5,0.5,\zlevel) .. (1.5,1.5,\zlevel)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Na \p){}
  		}
  	.. controls  (0.5,2.5,\zlevel) .. (P1.center)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Ma \p){}
  		}
  		;

  	%Curva Variata
    \draw[gray,line width=0.5pt,dotted] (1 ,0,\zlevel)
    .. controls (1.95,0.75,1.75)  and (2.8,0.5,2.5) .. (2.25,1.5,2.15)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Nb \p){}
  		}
  	.. controls  (1.5,2.5,\zlevel) .. (P2)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Mb \p){}
  		}
  		;
   	%Lo Jacobi Field
    \foreach \p in {0,2,...,8} {
      \draw[-latex,gray,line width=0.65pt,dotted] (Na \p.center) -- (Nb \p.center);
      \draw[-latex,gray,line width=0.65pt,dotted] (Ma \p.center) -- (Mb \p.center);    }

>>>>

\documentclass[border=10pt, tikz]{standalone}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
\usetikzlibrary{patterns,hobby}

@@

\draw[W] (O2.center) -- node [below] {} (A2.center); 
\draw[W] (A2.center) --  node [right] {} (B2.center);
\draw[W] (B2.center) --  node [right] {} (C2.center); 
\draw[W] (C2.center) --  node [above] {$V^\TwistedLinear F $} (O2.center);

\draw[W] (O.center) -- node [below] {} (O2.center); 
%\draw[W] (A.center) -- node [below] {} (A2.center); 
\draw[W] (B.center) -- node [below] {} (B2.center); 
\draw[W,hidden] (C.center) -- node [below] {} (C2.center);

@@

\node (P0) at (0.5,0,\zlevel) {};
\node (P1) at (1.2,3,\zlevel) {};
\node (P2) at (2.5,3,\zlevel)  {};

    	%Curva di Partenza
    \draw[red,line width=1pt] (P0.center)
    .. controls (1.5,0.75,\zlevel)  and (2.5,0.5,\zlevel) .. (1.5,1.5,\zlevel)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Na \p){}
  		}
  	.. controls  (0.5,2.5,\zlevel) .. (P1.center)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Ma \p){}
  		}
  		;

  	%Curva Variata
    \draw[purple,line width=0.5pt,dotted] (P0)+(0.25,0,0)
    .. controls (1.95,0.75,\zlevel)  and (2.8,0.5,\zlevel) .. (2.35,1.5,\zlevel)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[pos=\p/10]
      			(Nb \p){}
  		}
  	.. controls  (1.5,2.5,\zlevel) .. (P2.center)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[pos=\p/10]
      			(Mb \p){}
  		}
  		;
   	%Lo Jacobi Field
    \foreach \p in {0,2,...,10} {
      \draw[->,orange,line width=0.65pt] (Na \p.center) -- (Nb \p.center);
      \draw[->,orange,line width=0.65pt] (Ma \p.center) -- (Mb \p.center);    }

      \node (p) at (1.2,3,\zlevel) [below right,red] {$D[\phi]$};
	  \node (q) at (2.5,3,\zlevel)  [below right,purple] {$D[\phi_\lambda]$};
	  \node (r) at (Mb 0)  [above,orange] {$\delta D[\phi]$};

\draw[W] (A.center) -- node [below] {} (A2.center); 
\path[fill=green!5,opacity=.25] (B.center) to (A.center) to (A2.center) to (A2.center) to (B.center);
\path[fill=green!5,opacity=.25] (A.center) to (O.center) to (O2.center) to (O2.center) to (A.center);

@@
